Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
df <- fen %>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

>>>>

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
df <- fen %>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
